\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-10 paper/fse23/intro.tex
intro

 However, existing linguistic capability-based testing approaches rely
 on manually generated input templates, which need to be preset before
 generating tests.  As a result, these templates are limited in their
 sentence structures. This restricts existing approaches' ability to
 comprehensively test linguistic capabilities.

>>>>

However, existing linguistic capability-based testing approaches
generate inputs only relying on word substitution, and need to be
preset before generating tests.  As a result, these templates are
limited in their sentence structures. This restricts existing
approaches' ability to comprehensively test linguistic capabilities.
